Collocated Deduplication with Fault Isolation for Virtual Machine Snapshot Backup

### 2013-06-11 snapshot_system/snapshot.tex
modif

\begin{itemize}
\item \textbf{Dirtybit-based corase-grain inner-VM deduplication.}
The first-level deduplication is to follow the standand dirty bit approach, but is conducted
in the coarse grain segment level.
We use the  Xen virtual device driver which supports dirty bits for thestorage device
and the dirty bit setting is maintained in a corase grain level we call it a segment.
In our implementation, the segment size is 2MB. 
Since every write for a block will touch a dirty bit, the device driver maintains dirtybits in memory
and cannot affort a small segment  size.

>>>>

\begin{itemize}
\item \textbf{Dirtybit-based corase-grain inner-VM deduplication.}
The first-level deduplication is to follow the standand dirty bit approach, but is conducted
in the coarse grain segment level.
We use the  Xen virtual device driver which supports changed block tracking
for the storage device
and the dirty bit setting is maintained in a corase grain level we call it a segment.
In our implementation, the segment size is 2MB. 
Since every write for a block will touch a dirty bit, the device driver maintains dirtybits in memory
and cannot affort a small segment  size.

It should be noted that changed block tracking is supported or can be easily implemented in several 
major virtualization solution vendors. 
%(VMware, Xen, Microsoft).  
VMware support it directly. Their hypervisor has API to let external backup application know 
the changed areas since last backup.  Xen doesn't directly support it. However, their open-source 
architecture allows anyone to extend the device driver, thus enabling changed block tracking. 
We implements this way in the Alibaba's platform.  
Microsoft SDK provides an API that allows external application monitor 
the VM's I/O traffic.  Therefore changed block tracking can be implemented externally.
